\documentclass[11pt,letter]{moderncv}
\usepackage{newtxtext}    %% or newtxtext for times 

% style
\moderncvstyle{banking}
\moderncvcolor{black}

% character encoding
% \usepackage[utf8]{inputenc}

% margins and page layout
\usepackage[scale=0.9]{geometry}
\nopagenumbers
\recomputelengths

% personal data
\firstname{Connor}
\familyname{Brubaker}
\address{College Station, TX}{}
\mobile{(737) 217 - 3632}
\email{brubaker@tamu.edu}
\social[linkedin]{connorbrubaker}
\social[github]{brubakerconnor}

\begin{document}
\maketitle

% summary
\section{Summary}
Ph.D. candidate in statistics with expertise in time series analysis, spatial statistics, and machine learning and strong proficiency in R and Python. Thrives in interdisciplinary collaborative environments aimed at solving complex problems and seeks a role in designing well-crafted statistical solutions for automation and discovery. 

% education
\section{Education}
\cventry{2025}{Ph.D. in Statistics}{Texas A\&M University}
    {College Station, Texas}{}{}
\cventry{2019}{B.S. in Mathematics}{The University of Texas at Austin}
    {Austin, Texas}{}{}

% work experience
\section{Experience}
\cventry{Jun. 2022 - Aug. 2022}{Data Science Intern}{Liberty Mutual Insurance}{Boston, MA}{}{
\begin{itemize}
    \item Restructured and performed morphological and syntactic analysis on large, annotated text corpora using R and Python.
    \item Designed and validated hierarchical machine learning models based on transformers for automatic underwriting risk segmentation.
\end{itemize}
}

\cventry{Dec. 2019 - Jul. 2020}{Engineering Research Associate}{Applied Research Laboratories}{Austin, TX}{}{
\begin{itemize}
    \item Implemented deep learning models for online object-tracking in sonar images using transfer learning.
    \item Developed and trained convolutional neural network-based models for dimensionality reduction and clustering of image data.
    \item Developed educational materials for an internal course on machine learning.
\end{itemize}
}

\cventry{May 2019 - Aug. 2019}{Data Intern}{Alerian}{Dallas, TX}{}{
\begin{itemize}
    \item Developed automated reporting and backtesting processes in Visual Basic, enhancing accuracy and significantly reducing time costs.
    \item Applied time series forecasting and causal inference to evaluate the impact of marketing budget changes on website traffic and sales.
\end{itemize}
}

% teaching experience
% \section{Teaching Experience}
% \cventry{Spring 2024}{STAT 211: Principles of Statistics I}{Texas A\&M University}{}{}{}
% \cventry{Fall 2021}{STAT 302: Statistical Methods}{Texas A\&M University}{}{}{}

% publications
\nocite{*}
\bibliographystyle{plain}
\bibliography{Publications}

% collaborative projects
\section{Collaborative Projects}
\cventry{2024}{Collaboration with the Department of Geology \& Geophysics at Texas A\&M}{Survey Analysis of K-12 Teacher Sentiment Towards AI in Education}{}{}{}
\cventry{2024}{Collaboration with the Department of Atmospheric, Oceanic \& Earth Sciences at George Mason University}{Automatic Storm Track Identification via Spatiotemporal Regionalization of Weather Data}{}{}{}
\cventry{2024}{Collaboration with the Department of Entomology at Texas A\&M}{Quasi-Poisson Regression Analysis of Fly Production Data}{}{}{}
\cventry{2024}{Collaboration with the Department of Industrial \& Systems Engineering at Texas A\&M}{Cluster Analysis of EOG Measurements for the Detection of Fatigue}{}{}{}
\cventry{2023}{Collaboration with the Natural Resources Institute at Texas A\&M}{Analysis of Home Range and Ecological Needs of the Western Chicken Turtle}{}{}{}
\cventry{2022}{Collaboration with the College of Medicine at Texas A\&M}{Meta-Analysis on the Link between Tissue Origin and Role of Dkk-1 in Cancer Progression}{}{}{}

% teaching
\section{Teaching}
\cvlistitem{Instructor for STAT 211, Principles of Statistics I. Spring 2022.}
\cvlistitem{Instructor for STAT 302, Statistical Methods. Fall 2021.}
\cvlistitem{TA for STAT 673, Time Series Analysis I. Fall 2024.}
\cvlistitem{TA for STAT 652, Statistics in Research II. Summer 2021.}
\cvlistitem{TA for STAT 611, Theory of Statistical Inference. Spring 2021.}
\cvlistitem{TA for STAT 608, Regression Analysis. Fall 2020.}

% presentations
\section{Presentations}
\cventry{August 2024}{Contributed Talk}{Joint Statistical Meetings 2024}{Portland, OR}{}{}
\cventry{August 2023}{Contributed Talk}{Joint Statistical Meetings 2023}{Toronto, ON, CA}{}{}
\cventry{June 2023}{Poster}{SRCOS Summer Research Conference}{Waco, TX}{}{}
\cventry{May 2023}{Poster}{SETCASA Poster Competition}{College Station, TX}{}{}

% awards and recognition
\section{Awards \& Recognition}
\cventry{2023}{Travel Award}{SRCOS Summer Research Conference}{Waco, TX}{}{}
\cventry{2023}{Silver Award}{SETCASA Poster Competition}{College Station, TX}{}{}
\cventry{2022}{Nominated for College of Science Award for 
    Outstanding Achievement in Graduate Teaching}{Texas A\&M University}
    {College Station, TX}{}{}

% service
\section{Service}
\cventry{April 2024}{Guest Lecturer}{ASA DataFest at Southern Methodist University}{Dallas, TX}{}{}
\cventry{June 2023}{Volunteer Instructor}{Department of Statistics Data Science Summer Camp}{College Station, TX}{}{}

% professional organizations
\section{Professional Organizations}
\cvlistitem{American Statistical Association}
\cvlistitem{International Chinese Statistical Association}
\cvlistitem{American Guild of Organists}

% skills
\section{Skills}
\cvline{Software}{R, Python, TensorFlow, PyTorch, C++, SQL, Shell, Git, Docker, AWS}
\cvline{Statistical}{Time series analysis, regression analysis, spatial statistics, machine learning, natural language processing, cluster analysis, Bayesian methodology, statistical modeling}

\end{document}